### 2015-05-14 background.tex
fixes
fix

Lockset analysis is a lightweight race detection method proposed in the context of Eraser~\cite{savage1997eraser}, a dynamic data race detector.  The idea is to track the set of locks that are \emph{consistently} used to protect a memory location during program execution. If that lockset ever becomes empty, the analysis reports a \emph{potential} race on that memory location. This is because an inconsistent lockset suggests that a memory location \emph{may} be accessed simultaneously by two or more threads.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{img/lockset.pdf}
\caption{Applying lockset analysis on a thread of a concurrent program}
\label{fig:locksets}
\end{figure}

>>>>

Lockset analysis is a lightweight race detection method proposed in the context of Eraser~\cite{savage1997eraser}, a dynamic data race detector.  The idea is to track the set of locks that are \emph{consistently} used to protect a memory location during program execution. If that lockset ever becomes empty, the analysis reports a \emph{potential} race on that memory location. This is because an empty lockset suggests that a memory location \emph{may} be accessed simultaneously by two or more threads.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{img/lockset.pdf}
\caption{Applying lockset analysis on a concurrent program}
\label{fig:locksets}
\end{figure}
